Installation of Required Software

### 2021-01-12 README.Rmd
usethis::use_code_of_conduct()
add 'concept'-badge

# A quick tour through the `repro`-package

@@

>>>>

# A quick tour through the `repro`-package
<!-- badges: start -->
[![Project Status: Concept – Minimal or no implementation has been done yet, or the repository is only intended to be a limited example, demo, or proof-of-concept.](https://www.repostatus.org/badges/latest/concept.svg)](https://www.repostatus.org/#concept)
<!-- badges: end -->

@@

## Code of Conduct

Please note that the repro-tutorial project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
